---
title: "Exploratory Data Analysis by Skandarajan Rajaratnam"
output:html_notebook: default
output:html_document: default
---

## Introduction

Exploring the univariate, bivariate, & multivariate relationships between variables with data analysis techniques in R. This tidy data set contains 1,599 red wines with 11 variables on the chemical properties of the wine.

Number of Instances: Red wine - 1599 

Number of Attributes: 11 + output attribute

Input variables (based on physicochemical tests):

   1 - fixed acidity (tartaric acid - g / dm^3): Most acids involved with wine or fixed or nonvolatile. 
   
   2 - volatile acidity (acetic acid - g / dm^3): The amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste
   
   3 - citric acid (g / dm^3): Found in small quantities, citric acid can add 'freshness' and flavor to wine
   
   4 - residual sugar (g / dm^3): The amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet
   
   5 - chlorides (sodium chloride - (g / dm^3): The amount of salt in the wine
   
   6 - free sulfur dioxide (mg / dm^3): The free form of SO2 exists in equilibrium between molecular SO2 and bisulfite ion; it prevents microbial growth and the oxidation of wine
   
   7 - total sulfur dioxide (mg / dm^3): Amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine
   
   8 - density (g / cm^3): The density of water is close to that of water depending on the percent alcohol and sugar content
   
   9 - pH: Describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale
   
   10 - sulphates (potassium sulphate - g / dm3): A wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant
   
   11 - alcohol (% by volume): The percent alcohol content of the wine.
   
Output variable (based on sensory data):

   12 - quality (score between 0 and 10)
   
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
#install.packages('plyr')
#install.packages('GGally')
#install.packages('scales')
#install.packages('lattice')
#install.packages('MASS')
#install.packages('car')
#install.packages('reshape')
#install.packages('plyr')
#install.packages("ggcorrplot")

library(ggplot2)
library(GGally)
library(scales)
library(dplyr)
library(gridExtra)
```
Required Packages ara loaded.
```{r echo=FALSE, Load_the_Data}
# Load the data
setwd("C:\\Users\\Skanda\\Desktop\\DANDJ\\EDA-P4")

wineRed <- read.csv('wineQualityReds.csv')

head(wineRed)

tail(wineRed, 10)

str(wineRed)
```
Structure of the dataset?

The dataset is contains 1,599 observations with 11 variables.Variables are of classes integer and numeric. The quality is scored in numbers. I am creating a new variable called "total_acidity". Also creating a "quality_bucket" categorical varible to analyse the quality of the wine as a grroup.

# Univariate Plots Section

```{r echo=FALSE, Univariate_Plots}
# I try to get more about dataset, How are they related to each other. I am trying to get a pattern and the behaviour of each features.

W1 <- qplot(data = wineRed, x = pH , binwidth = .1,  color = I('black'), fill = I('#099DD9')) +
        xlab('pH') +
        ylab('Wine Count')
W1
# ph is a bell curve with the number of wine. It is a standard normal distribution. 

#Adjusting The Bin Width
W2 <- qplot(data = wineRed, x = fixed.acidity , binwidth = 1,  color = I('black'), fill = I('#099DE9')) +
        xlab('Fixed.acidity') +
        ylab('Wine Count')
W2
# Fixed acidity is rught skewed with wine count

W3 <- qplot(data = wineRed, x = volatile.acidity , xlim = c(0,1.5), binwidth = .1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Volatile.acidity') +
        ylab('Wine Count')
W3
# Volatility is also has a Standard normal distribution with the wine count.

W4 <- qplot(data = wineRed, x = citric.acid, binwidth = .1,  color = I('black'), fill = I('#099FF9')) +
        xlab('Citric.acid') +
        ylab('Wine Count')

W5 <- qplot(data = wineRed, x = residual.sugar, binwidth = .1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Residual.sugar') +
        ylab('Wine Count')

W6 <- qplot(data = wineRed, x = chlorides, binwidth = .01,  color = I('black'), fill = I('#099EE9')) +
        xlab('Chloride') +
        ylab('Wine Count')

W7 <- qplot(data = wineRed, x = free.sulfur.dioxide, binwidth = 1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Free.sulfur.dioxide') +
        ylab('Wine Count')

W8 <- qplot(data = wineRed, x = total.sulfur.dioxide, binwidth = 10,  color = I('black'), fill = I('#099EE9')) +
        xlab('Total.sulfur.dioxide') +
        ylab('Wine Count')

W9 <- qplot(data = wineRed, x = alcohol, binwidth = .1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Alcohol(%)') +
        ylab('Wine Count')
W9

W10 <- qplot(data = wineRed, x = as.numeric(quality), binwidth = .1,color = I('black'), fill = I('#099EE9')) +
        xlab('Quality') +
        ylab('Wine Count')
W10

# Citric acid does not seems to be vary with the wine count.
# Residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide are right skewed distribution with the wine count.They are long tailed in the right side. 
# Medium quality wine are double trible the count than low and high quality. Seems like normaly distributed.
# No variation in the density.

W11 <- qplot(data = wineRed, x = density, binwidth = 1,color = I('black'), fill = I('#099EE9')) +
        xlab('Density') +
        ylab('Wine Count')
       
grid.arrange(W1, W2, W3, W4, W5, W6, W7, W8, W9, W10, W11, ncol = 3)

```


1. Citric acid does not seems to be vary with the wine count.

2. Residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide are right skewed distribution with the wine count.They are long tailed in the right side. 

3. Medium quality wine are double trible the count than low and high quality. Seems like normaly distributed.

4. No variation in the density.

Calculate Total acids in the red wines, I create a new variable called total_acidity.
```{r echo=FALSE, Univariate_Plots1}

wineRed$total_acidity <- wineRed$fixed.acidity + wineRed$volatile.acidity + wineRed$citric.acid
head(wineRed$total_acidity)

ggplot(aes(x = total_acidity), data = subset(wineRed, !is.na(total_acidity))) + geom_histogram() +
        xlab('Total Acid') +
        ylab('Wine Count') + scale_x_log10()

```


Total acid in the wine is a nominaly distributed. 

Quality of wine 
It is scored by numbers 0 - 10. I am going to make a bucket

 0-3:  Low Quality
 
 4-6:  Medium Quality
 
 7-10: High Quality

Transform quality from an integer to a categorical parameter.

```{r echo=FALSE, Univariate_Plots2} 
wineRed$quality <- factor(wineRed$quality, ordered = T)

wineRed$quality_bucket <- ifelse(wineRed$quality <= 3,
                                 'Low Quality',
                                 ifelse(wineRed$quality <= 6,
                                        'Medium Quality',
                                        'High Quality'))

wineRed$quality_bucket <- ordered(wineRed$quality_bucket,
                     levels = c('Low Quality', 'Medium Quality', 'High Quality'))

head(wineRed$quality_bucket)

ggplot(aes(x = quality_bucket), data = wineRed) + geom_bar(aes(fill = quality)) +
        xlab('Wine Quality') +
        ylab('Wine Count')
```


From the plot, we can see medium quality wine are produced more or more in demand in the market place.

# Univariate Analysis

#### 1. What is the structure of your dataset?
The dataset is contains 1,599 observations with 11 variables.Variables are of classes int and numeric. The quality is scored in numbers. I am creating a new variable called "total_acid". Also creating a quality_bucket categorical varible.
Total 1,599 observationa and 13 Variables.

#### 2. What is/are the main feature(s) of interest in your dataset?
Taste / Tactile - The tongue only can sense taste and feel texture. It senses sweetness (the presence of sugar), sourness (the presence of acidity), bitterness and saltiness. In addition, it can feel heat from alcohol. I am interested in how these 11 varibleas are influnceing the above senses. Mainly how the acidity and the percentage of alcohol influencing the tase and the quality of the red wine. How the risidual sugar has influence the sweet and quality of the wine.
I'd like to determine which features are best for predicting the quality of the Red wine and also which factor bring more demand on red wines.

#### 3. What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

I think acidity, sulfur, residual sugar, sulphates and alcohol are likely contribute to the quality of wine. I think acidity and sulfur probably contribute most to the quality of the wine.

#### 4. Did you create any new variables from existing variables in the dataset?
I created a variable for the total acidity of the red wine to analyze how the acidity influencing the wine quality. Also created categorical variable "quality _bucket" to have the quality to classify the wines into 3 categories Low, Midium and High Quality.

#### 5. The features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
Yes, I did see outliers on some plots and did use limit the scale. Observed some graphs fixed acidity, free sulfur dioxide, total sulfur dioxide and alcohol % are Right skewed distribustion and others seems to be Normal distribution as bell curve. 
Also tried the log10 base to see any abnomalities 

# Bivariate Plots Section

Looking at the ggcorr and ggpairs matrix, I observed some interesting relationships between the following variables:

We can see strong relation ship betwwen
fixed acidity Vs density (0.7)
fixed acidity  Vs citric acid (0.7)
fixed acidity Vs pH (-0.7)
Alcohol Vs density (-0.5)

```{r echo=FALSE, Bivariate_Plots}
summary(wineRed)
library(ggplot2)
library(GGally)
library(scales)
library(ggcorrplot)

ggcorr(wineRed[, 2:12], label = TRUE, method = c("pairwise", "pearson"))


pw <- ggpairs(wineRed, lower = list(continuous = wrap("points", shape = I('.'))),
        upper = list(combo = wrap("box", outlier.shape = I('.'))))

pw
pw1 <- ggpairs(wineRed, columns = c("quality", "alcohol", "total.sulfur.dioxide", "total_acidity"),
               columnLabels = c("quality", "alcohol", "total.sulfur.dioxide", "total_acidity"))

pw1

# 1. Quality Vs Alcohol
ggplot(aes( x=quality_bucket, y=alcohol), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
# High quality wine has high alcohol % compare to medium and low. Increasing Alcohol % the quality of the wine is high.

ggplot(aes(x = alcohol, y = density), data = wineRed) + 
        geom_jitter(alpha = 1/4, shape = 21, fill = I('#099373')) + geom_smooth()

ggplot(aes( x=quality_bucket, y=density), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
# From above plots, Density is increasing with alcohol %. Quality is increasing with the % of alcohol, But quality of the wine is decreasing with density.

# 2. Fixed acidity Vs pH
ggplot(aes(x = fixed.acidity, y = pH), data = wineRed) + 
        geom_jitter(alpha = 1/4, shape = 21, fill = I('#099373')) + geom_smooth(method = "lm",level = 0.99, se=TRUE)

cor.test(wineRed$pH,wineRed$fixed.acidity, method = 'pearson')
# From The plot, pH level is decreasing with increasing "fixed acidity"

# 3. Fixed acidity Vs Citric acid
ggplot(aes(x = fixed.acidity, y = citric.acid), data = wineRed) + 
        geom_jitter(alpha = 1/4, shape = 21, fill = I('#099373')) + geom_smooth(method = "lm",level = 0.99, se=TRUE)

cor.test(wineRed$citric.acid, wineRed$fixed.acidity, method = 'pearson')
# Fixed acidity increasing with citric acid.

```
1. Quality Vs Alcohol - High quality wine has high alcohol % compare to medium and low. Increasing Alcohol % the quality of the wine is high. Density is increasing with alcohol %. Quality is increasing with the % of alcohol, But quality of the wine is decreasing with density.

2. Fixed acidity Vs pH - From the plot, pH level is decreasing with increasing "fixed acidity"

3. Fixed acidity Vs Citric acid - Fixed acidity increasing with citric acid.

I am seeing outliers on the medium quality red wines. Also high quality red wine average alcohol contain is more that midium and low quality red wines.

Quality Vs Total Acidity

```{r echo=FALSE, Bivariate_Plots1}

pwaT <- ggplot(aes( x=quality_bucket, y=total_acidity), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
pwaT

# Analyze the corelation of each acidity with quality 

pwaV <- ggplot(aes( x=quality_bucket, y=volatile.acidity), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
pwaV

pwaC <- ggplot(aes( x=quality_bucket, y=citric.acid), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
pwaC

pwaF <- ggplot(aes( x=quality_bucket, y=fixed.acidity), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
pwaF

grid.arrange(pwaC , pwaV, pwaF, pwaT, ncol = 2)
```


Red wine Quality is increasing with citric acid and fixed acidity but decreasing with volatile acidity.  

Look at the relationship betewwn the quality and sulfur dioxide

```{r echo=FALSE, Bivariate_Plots2}

pwS1 <- ggplot(aes(x = quality_bucket, y = total.sulfur.dioxide), data = wineRed) + 
        geom_boxplot()

# Medium quality has more total sulfur dioxide and low quality has less sulfur. I am not seing any correlation between the quality and the total sulfur.

pwS2 <- ggplot(aes(x = quality_bucket, y = free.sulfur.dioxide), data = wineRed) + 
        geom_boxplot()

sulfur <- wineRed$free.sulfur.dioxide + wineRed$total.sulfur.dioxide

pwS <- ggplot(aes(x = quality_bucket, y = sulfur), data = wineRed) + 
        geom_boxplot()
grid.arrange(pwS1, pwS2, pwS, ncol= 3)
```


Medium quality has more total sulfur dioxide and low quality has less sulfur. I am not seing any correlation between the quality and the total sulfur.

Quality Vs Residual SUgar - Observed outliers in the midium and High quality wine.

```{r echo=FALSE, Bivariate_Plots3}
ggplot(aes( x = quality_bucket , y = residual.sugar), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
```

# Bivariate Analysis

#### 1. Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

Looking at the ggcorr and ggpairs matrix, I observed some interesting relationships between the following variables:

We can see strong coorelation betwwen the following variable in the dataset
fixed acidity Vs density (0.7)
fixed acidity  Vs citric acid (0.7)
fixed acidity Vs pH (-0.7)
Alcohol Vs density (-0.5)
 
#### 2. Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
The density is strongly correlated with two other features: residual sugar (positively), and alcohol (negatively). It makes sense, taking into account the fermentation process of wine, in which sugar is consumed to generate alcohol.

#### 3. What was the strongest relationship you found?
Percentage of Alcohol variable has the strongest relationship with quality. High quality wine has high alcohol % compare to medium and low. Increasing percentage of Alcohol, the quality of the wine is high.

# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}
# Quality with Alcohol and Residual Sugar
ggplot(aes(x= residual.sugar , y = alcohol), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)       

# Quality score is moving upward with increase of % of alcohol and residual sugar. But one of the quality score-6 is varying from others. Which is moving downward with increasing value of alcohol % and residual sugar

# Quality with Alcohol and density
ggplot(aes(x= alcohol, y = density), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)

# Quality score moving downword with the increase of alcohol and decresing of density

# Quality with Fixed acidity and pH
fa1 <- ggplot(aes(x= fixed.acidity , y = pH), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)

# Quality score is moving downward with pH and fixed acidity

# Quality with Fixed acidity and Citric acid
fa2 <- ggplot(aes(x= fixed.acidity , y = citric.acid), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)

# Quality score is moving upward with Citric acid and fixed acidity

# Quality with Fixed acidity and Density
fa3 <- ggplot(aes(x= fixed.acidity , y = density), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)

#Quality score is moving upward with density and fixed acidity

grid.arrange(fa1, fa2, fa3, ncol = 3)
```


1. Quality score is moving upward with increase of % of alcohol and residual sugar. But one of the quality score-6 is varying from others. Which is moving downward with increasing value of alcohol % and residual sugar.

2. Quality score moving downword with the increase of alcohol and decresing of density.

3. Quality score is moving downward with pH and fixed acidity.

4. Quality score is moving upward with Citric acid and fixed acidity.

5. Quality score is moving upward with density and fixed acidity.

```{r echo=FALSE, Multivariate_Plots1}

wineRed$Quality <- as.numeric(wineRed$quality)

m1 <- lm(I(log(Quality)) ~ I(density^(1/3)), data = wineRed)
#m1 <- lm(Quality ~ alcohol, data = wineRed)                
         
m2 <- update(m1, ~ . + alcohol)
m3 <- update(m2, ~ . + volatile.acidity)
m4 <- update(m3, ~ . + fixed.acidity)
m5 <- update(m4, ~ . + total.sulfur.dioxide)
m6 <- update(m5, ~ . + residual.sugar)
m7 <- update(m6, ~ . + citric.acid)

summary(m7)

```

# Multivariate Analysis

#### 1. Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?
I analyzed the relationship between quality and other feature variables in the dataset. The alcohol,density and residual sugar had strong relationship with each other and increasing the quality on the wine. I am seeing quality score has a linear relationship with alcohol, volatile.acidity, fixed.acidity, residual.sugar and citric.acid.

There are number of outliers for medium quality scores 5 & 6, also seeing small number of ouliers for high quality score 7 & 8. I am seeing that the Quality increases when the % of alcohol increases. But, I am not seeing significant correlation from the linear model. I am seeing significant level of (p-value) Pr = 0.908 for density and Pr = 0.999 for residual.sugar. These variables were amongst the most important predictors in the linear model built.

#### 2. Were there any interesting or surprising interactions between features?
Yes, Quality is increases when the % of alcohol increases. But, I am not seeing significant correlation from the linear model. 
95 percent confidence interval: 0.4373540  - 0.5132081

#### 3. OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.\

I created a linear model for predicting quality of wine. Adjusted R-squared:  0.2882, which is low. R-squard: 1 is strong in prediction. It indicates that a linear model is not the best model for this dataset. The folowing Variables residual sugar, alcohol, citric acid, volatile acidity and density are influencing the prediction.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
wineRed$quality <- factor(wineRed$quality, ordered = T)


wineRed$quality_bucket <- ifelse(wineRed$quality <= 3,
                                 'Low Quality',
                                 ifelse(wineRed$quality <= 6,
                                        'Medium Quality',
                                        'High Quality'))
wineRed$quality_bucket <- ordered(wineRed$quality_bucket,
                     levels = c('Low Quality', 'Medium Quality', 'High Quality'))

ggplot(aes(x = quality_bucket), data = wineRed) + geom_bar(aes(fill = quality)) +
        xlab('Wine Quality') +
        ylab('Wine Count') +
        ggtitle('Quality Of Red Wine')

```

### Description One
Above ggplot tell us the industry producing Low, Medium and High Quality of Red wines. Also we can see the demand for the quality of the wine.
Medium wine are in more demand than High quality and Low quality red wine.  

### Plot Two
```{r echo=FALSE, Plot_Two}

ggcorr(wineRed[, 2:12], label = TRUE, method = c("pairwise", "pearson"))

```

### Description Two
In this ggcorr plot, we observe various amounts of correlations among variables. For instance, there is a very
strong positive correlation between total sulfur dioxide and free sulfur dioxide. Similarly, density is positively 
correlated with fixed acidity and residual sugar. On the other hand, it has a strong negative correlation with
alcohol.
The colors give us a clear visualization of, how the variable are correlated to each other features. -1(low) to 1.0 ( high) correlation coefficients with the color indication.
Example, we can see strong positive relation ship betwwen fixed acidity Vs density (0.7), fixed acidity  Vs citric acid (0.7) and negative relationship between fixed acidity Vs pH (-0.7), Alcohol Vs density (-0.5).

All these correlations intuitively make sense. Strong correlations mean that these correlated variables
should be handled carefully in a learning model. Possibly, some of them can be dropped out depending on
which ones carry the highest importance.

### Plot Three
```{r echo=FALSE, Plot_Three}

ggplot(aes(x= residual.sugar , y = alcohol), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE) +
        xlab('Residual Sugar (g / dm^3)') +
        ylab('Alcohol (% by volume)') +
        ggtitle('Quality of The Red Wine by Alcohol and Residual Sugar')

```

### Description Three
Looking at the plot, We can notice that the High Quality of the wine has more residual sugar and more alcohol and the trend is linearly upward. Low quality wine has less residualsugar and % of alcohol is also less and the quality trend is linearly upward. Medium quality wine has an interesting behaviour, It has more residual sugar and the trend is lenear. But I am seeing 2 different linearlity. Scored 5 one is positive or in upward direction with alcohol and residual sugar, but the score 6 one is in negative or in downward direction.

------

# Reflection
This explores the univariate, bivariate, & multivariate relationships between variables. This data set contains 1,599 red wines with 11 variables on the chemical properties of the wine.

Residual Sugar - This is the amount of sugar left in solution after fermentation has finished. Residual sugar and density have a positive strong correlation. R-squard: Pr values 0.99 and 0.91 accordingly. In wine tasting, the term "acidity" refers to the fresh, tart and sour attributes of the wine which are evaluated in relation to how well the acidity balances out the sweetness and bitter components of the wine.

I identified Residual sugar, Alcohol, Acidity and Density are strongly correlated togheter influencing the quality of the wine.Alcohol content appeared to be the number one factor for determining a high quality wine. Citric acid and Sulphates had to be in specific amounts in order for alcohol to influence the taste or quality of the wine.

I observed, Wine with high percent of alcohol content and total acidity tends to be rated as high quality wine. Also wine with low % of alcohol with more total acidity tends to be rated as low quality wine. Based on the result, we can see that the acidity in wine and percent alcohol content are two important components in the quality and taste of Red wine.

References:

https://www.statmethods.net/

https://briatte.github.io/ggcorr/#controlling-the-coefficient-labels

https://en.wikipedia.org/wiki/Acids_in_wine




