---
title: "Exploratory Data Analysis"
author: Skandarajan Rajaratnam
date: 02/10/2018
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

## Introduction

Exploring the univariate, bivariate, & multivariate relationships between 
variables with data analysis techniques in R. This tidy data set contains 
1,599 red wines with 11 variables on the chemical properties of the wine.

Number of Instances: Red wine - 1599 

Number of Attributes: 11 + output attribute

Input variables (based on physicochemical tests):

   1 - fixed acidity (tartaric acid - g / dm^3): Most acids involved with wine
   or fixed or nonvolatile. 
   
   2 - volatile acidity (acetic acid - g / dm^3): The amount of acetic acid in
   wine, which at too high of levels can lead to an unpleasant, vinegar taste
   
   3 - citric acid (g / dm^3): Found in small quantities, citric acid can add
   'freshness' and flavor to wine
   
   4 - residual sugar (g / dm^3): The amount of sugar remaining after 
   fermentation stops, it's rare to find wines with less than 1 gram/liter and
   wines with greater than 45 grams/liter are considered sweet
   
   5 - chlorides (sodium chloride - (g / dm^3): The amount of salt in the wine
   
   6 - free sulfur dioxide (mg / dm^3): The free form of SO2 exists in 
   equilibrium between molecular SO2 and bisulfite ion; it prevents microbial
   growth and the oxidation of wine
   
   7 - total sulfur dioxide (mg / dm^3): Amount of free and bound forms of S02;
   in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 
   concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine
   
   8 - density (g / cm^3): The density of water is close to that of water 
   depending on the percent alcohol and sugar content
   
   9 - pH: Describes how acidic or basic a wine is on a scale from 0 (very acidic)
   to 14 (very basic); most wines are between 3-4 on the pH scale
   
   10 - sulphates (potassium sulphate - g / dm3): A wine additive which can 
   contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial
   and antioxidant
   
   11 - alcohol (% by volume): The percent alcohol content of the wine.
   
Output variable (based on sensory data):

   12 - quality (score between 0 and 10)
   
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
#install.packages('plyr')
#install.packages('GGally')
#install.packages('scales')
#install.packages('lattice')
#install.packages('MASS')
#install.packages('car')
#install.packages('reshape')
#install.packages('plyr')
#install.packages("ggcorrplot")

library(ggplot2)
library(GGally)
library(scales)
library(dplyr)
library(gridExtra)
```
Required Packages ara loaded.
```{r echo=FALSE, Load_the_Data}
# Load the data
setwd("C:\\Users\\Skanda\\Desktop\\DANDJ\\EDA-P4")

wineRed <- read.csv('wineQualityReds.csv')

head(wineRed)

tail(wineRed, 10)

str(wineRed)
```
Structure of the dataset?

The dataset is contains 1,599 observations with 11 variables.Variables are of 
classes integer and numeric. The quality is scored in numbers. I am creating 
a new variable called "total_acidity". Also creating a "quality_bucket" 
categorical varible to analyse the quality of the wine as a grroup.

# Univariate Plots Section

```{r echo=FALSE, Univariate_Plots}

W1 <- qplot(data = wineRed, x = pH , binwidth = .1,  color = I('black'), fill = I('#099DD9')) +
        xlab('pH') +
        ylab('Wine Count')
#W1
grid.arrange(ggplot(wineRed, aes( x = 1, y = pH ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = pH  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

How acidic or basic a wine is on a scale from very acidic 0 to 14 very basic. ph
is normally distributed in the Red wine. It is a Standard normal distribution. 
Most wines are between 3-4 on the pH scale

```{r echo=FALSE, Univariate_Plots1}

W2 <- qplot(data = wineRed, x = fixed.acidity , binwidth = 1,  color = I('black'), fill = I('#099DE9')) +
        xlab('Fixed.acidity') +
        ylab('Wine Count')
#W2

grid.arrange(ggplot(wineRed, aes( x = 1, y = fixed.acidity ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = fixed.acidity  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

The distribution of Fixed Acidity is positively skewed. The median is around 8 
with high concentration of wines with Fixed Acidity but due to some outliers, 
the mean has been dragged to around 9. 

```{r echo=FALSE, Univariate_Plots21}

W3 <- qplot(data = wineRed, x = volatile.acidity , xlim = c(0,1.5), binwidth = .1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Volatile.acidity') +
        ylab('Wine Count')
#W3
grid.arrange(ggplot(wineRed, aes( x = 1, y = volatile.acidity ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = volatile.acidity  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

The distribution of Volatile acidity looks like Bimodal with two peaks around 0.4 and 0.6.

```{r echo=FALSE, Univariate_Plots3}
W4 <- qplot(data = wineRed, x = citric.acid, binwidth = .1,  color = I('black'), fill = I('#099FF9')) +
        xlab('Citric.acid') +
        ylab('Wine Count')
#W4
grid.arrange(ggplot(wineRed, aes( x = 1, y = citric.acid ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = citric.acid  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

Apart from some outliers, the distribution of Citric acid looks strange. 
Some higher values have no data at all and apart from them, the distribution 
looks almost rectangular. 

```{r echo=FALSE, Univariate_Plots4}

W5 <- qplot(data = wineRed, x = residual.sugar, binwidth = 1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Residual.sugar') +
        ylab('Wine Count')

#W5

grid.arrange(ggplot(wineRed, aes( x = 1, y = residual.sugar ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = residual.sugar  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

The distribution of Residual Sugar is again positively skewed with high peaks at
around 2 with many outliers present at the higher ranges.

```{r echo=FALSE, Univariate_Plots5}
W6 <- qplot(data = wineRed, x = chlorides, binwidth = .1,  color = I('black'), fill = I('#099EE9')) +
        xlab('Chloride') +
        ylab('Wine Count')

#W6

grid.arrange(ggplot(wineRed, aes( x = 1, y = chlorides ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = chlorides  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

The distribution of Chorides is again positively skewed with high peaks at around
0.05 with many outliers present at the higher ranges.

```{r echo=FALSE, Univariate_Plots6}
W7 <- qplot(data = wineRed, x = free.sulfur.dioxide, binwidth = 10,  color = I('black'), fill = I('#099EE9')) +
        xlab('Free.sulfur.dioxide') +
        ylab('Wine Count')
#W7 

grid.arrange(ggplot(wineRed, aes( x = 1, y = free.sulfur.dioxide ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = free.sulfur.dioxide  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

Free Sulphur Dioxide, there is a high peak at 4.5 but then it again follows the 
same positively skewed long tailed patterns with some outliers in the high range.

```{r echo=FALSE, Univariate_Plots7}

W8 <- qplot(data = wineRed, x = total.sulfur.dioxide, binwidth = 10,  color = I('black'), fill = I('#099EE9')) +
        xlab('Total.sulfur.dioxide') +
        ylab('Wine Count')

W9 <- qplot(data = wineRed, x = alcohol, binwidth = .5,  color = I('black'), fill = I('#099EE9')) +
        xlab('Alcohol(%)') +
        ylab('Wine Count')
#W9
grid.arrange(ggplot(wineRed, aes( x = 1, y = alcohol ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = alcohol  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)

```

Alcohol also a skewed distribution. Here the skewness is less than that of 
Chlorides or Residual Sugars.

```{r echo=FALSE, Univariate_Plots8}
W10 <- qplot(data = wineRed, x = as.numeric(quality), binwidth = .5 ,color = I('black'), fill = I('#099EE9')) +
        xlab('Quality') +
        ylab('Wine Count')
#W10

grid.arrange(ggplot(wineRed, aes( x = 1, y = as.numeric(quality) ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = as.numeric(quality)  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)

grid.arrange(ggplot(wineRed, aes( x = 1, y = density ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = density  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)

grid.arrange(W1, W2, W3, W4, W5, W6, W7, W8, W9, W10, ncol = 3)

```


I try to get more about dataset, How are they related to each other. Also trying
to get a pattern and the behaviour of each features.
Noticed that the ph is a bell curve with the wine count. It is a Standard normal
distribution. The Fixed acidity is roughty skewed with wine count, Volatility 
is also has a Standard normal distribution with the wine count. Citric acid does
not seems to be vary with the wine count.

Residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide are right
skewed distribution with the wine count. They are long tailed in the right side.
Medium quality wine are double trible the count than low and high quality. Seems
like normaly distributed.No variation in the density.

Calculate Total acids in the red wines, I create a new variable called 
total_acidity.

```{r echo=FALSE, Univariate_Plots9}

wineRed$total_acidity <- wineRed$fixed.acidity + wineRed$volatile.acidity + wineRed$citric.acid
head(wineRed$total_acidity)

grid.arrange(ggplot(wineRed, aes( x = 1, y = total_acidity ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(wineRed, aes( x   = total_acidity  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


Total acid in the wine is a left skewed distributed. There is a high peak at 7.5   

Quality of wine 
It is scored by numbers 0 - 10. I am going to make a bucket

 0-3:  Low Quality
 
 4-6:  Medium Quality
 
 7-10: High Quality

Transform quality from an integer to a categorical parameter.

```{r echo=FALSE, Univariate_Plots10} 
wineRed$quality <- factor(wineRed$quality, ordered = T)

wineRed$quality_bucket <- ifelse(wineRed$quality <= 3,
                                 'Low Quality',
                                 ifelse(wineRed$quality <= 6,
                                        'Medium Quality',
                                        'High Quality'))

wineRed$quality_bucket <- ordered(wineRed$quality_bucket,
                     levels = c('Low Quality', 'Medium Quality', 'High Quality'))

head(wineRed$quality_bucket)

ggplot(aes(x = quality_bucket), data = wineRed) + geom_bar(aes(fill = quality)) + scale_fill_brewer(type='seq') + 
        xlab('Wine Quality') +
        ylab('Wine Count')

```

From the plot, we can see medium quality wine are produced more or more in 
demand in the market place.

# Univariate Analysis

#### 1. What is the structure of your dataset?
The dataset is contains 1,599 observations with 11 variables.Variables are of 
classes int and numeric. The quality is scored in numbers. I am creating a new
variable called "total_acid". Also creating a quality_bucket categorical varible.
Total 1,599 observationa and 13 Variables.

#### 2. What is/are the main feature(s) of interest in your dataset?
Taste / Tactile - The tongue only can sense taste and feel texture. It senses
sweetness (the presence of sugar), sourness (the presence of acidity), 
bitterness and saltiness. In addition, it can feel heat from alcohol.
I am interested in how these 11 varibleas are influnceing the above senses
. Mainly how the acidity and the percentage of alcohol influencing the tase
and the quality of the red wine. How the risidual sugar has influence the
sweet and quality of the wine.
I'd like to determine which features are best for predicting the quality of the
Red wine and also which factor bring more demand on red wines.

#### 3. What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

I think acidity, sulfur, residual sugar, sulphates and alcohol are likely 
contribute to the quality of wine. I think acidity and sulfur probably 
contribute most to the quality of the wine.

#### 4. Did you create any new variables from existing variables in the dataset?
I created a variable for the total acidity of the red wine to analyze how the
acidity influencing the wine quality. Also created categorical variable
"quality _bucket" to have the quality to classify the wines into 3 categories
Low, Midium and High Quality.

#### 5. The features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
Yes, I did see outliers on some plots and did use limit the scale. Observed some
graphs fixed acidity, free sulfur dioxide, total sulfur dioxide and alcohol %
are Right skewed distribustion and others seems to be Normal distribution as
bell curve. 
Also tried the log10 base to see any abnomalities 

# Bivariate Plots Section

Looking at the ggcorr and ggpairs matrix, I observed some interesting 
relationships between the following variables:

We can see strong relation ship betwwen
fixed acidity Vs density (0.7)
fixed acidity  Vs citric acid (0.7)
fixed acidity Vs pH (-0.7)
Alcohol Vs density (-0.5)

```{r echo=FALSE, Bivariate_Plots}
summary(wineRed)
library(ggplot2)
library(GGally)
library(scales)
library(ggcorrplot)

ggcorr(wineRed[, 2:12], label = TRUE, method = c("pairwise", "pearson"))

# 1. Quality Vs Alcohol
ggplot(aes( x=quality_bucket, y=alcohol), data = wineRed) + 
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)

ggplot(aes(factor(quality), 
            alcohol), 
        data = wineRed) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

High quality wine has high alcohol % compare to medium 
and low. Increasing Alcohol % the quality of the wine is high. Density is 
increasing with alcohol %. Quality is increasing with the % of alcohol, 
But quality of the wine is decreasing with density.


```{r echo=FALSE, Bivariate_Plots2}

#ggplot(aes( x=quality_bucket, y=density), data = wineRed) + 
#        geom_boxplot() +
#        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
ggplot(aes(factor(quality), 
            density), 
        data = wineRed) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

Better wines seems to have lower densities.Because there might be a possibility 
that the low density is due to higher alcohol content which actually is the 
driving factor for better wine.

```{r echo=FALSE, Bivariate_Plots3}

ggplot(aes(factor(quality), 
            citric.acid), 
        data = wineRed) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)

```

Citric acid seems to have a positive correlation with Wine Quality. Better wines
have higher Citric Acid.

```{r echo=FALSE, Bivariate_Plots4}

ggplot(aes(factor(quality), 
            volatile.acidity), 
        data = wineRed) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

Volatile acid seems to have a negative impact on the quality of the wine. 
As volatile acid level goes up, the quality of the wine degrades.

```{r echo=FALSE, Bivariate_Plots5}
#Fixed acidity Vs pH
ggplot(aes(x = fixed.acidity, y = pH), data = wineRed) + 
        geom_jitter(alpha = 1/4, shape = 21, fill = I('#099373')) + geom_smooth(method = "lm",level = 0.99, se=TRUE)

cor.test(wineRed$pH,wineRed$fixed.acidity, method = 'pearson')
```

Fixed acidity Vs pH - From the plot, pH level is decreasing with increasing
"fixed acidity"

```{r echo=FALSE, Univariate_Plots2}

#Fixed acidity Vs Citric acid
ggplot(aes(x = fixed.acidity, y = citric.acid), data = wineRed) + 
        geom_jitter(alpha = 1/4, shape = 21, fill = I('#099373')) + geom_smooth(method = "lm",level = 0.99, se=TRUE)

cor.test(wineRed$citric.acid, wineRed$fixed.acidity, method = 'pearson')

```

Fixed acidity Vs Citric acid - Fixed acidity increasing with citric acid.

I am seeing outliers on the medium quality red wines. Also high quality red wine
average alcohol contain is more that midium and low quality red wines.

Quality Vs Total Acidity

```{r echo=FALSE, Bivariate_Plots1}

pwaT <- ggplot(data = wineRed, aes(as.factor(quality), total_acidity, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("total_acidity")  +
        scale_fill_brewer(type = 'seq', palette = 1) 
pwaT

# Analyze the corelation of each acidity with quality 

pwaC <- ggplot(data = wineRed, aes(as.factor(quality), citric.acid, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("Citric Acid - g/dm^3")  +
        scale_fill_brewer(type = 'seq', palette = 1) 

pwaV <- ggplot(data = wineRed, aes(as.factor(quality), volatile.acidity, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("Volatile Acidity - g/dm^3") +
        scale_fill_brewer(type = 'seq', palette = 1)

pwaF <- ggplot(data = wineRed, aes(as.factor(quality), fixed.acidity, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("Fixed Acidity - g/dm^3") +
        scale_fill_brewer(type = 'seq', palette = 1)

grid.arrange( pwaC, pwaF, pwaV , ncol =1)


```

Analyze the corelation of each acidity with quality. Red wine Quality is 
increasing with citric acid and fixed acidity but decreasing with volatile
acidity.  

Look at the relationship between the quality and sulfur dioxide

```{r echo=FALSE, Bivariate_Plots6}

pwS1 <- ggplot(aes(x = quality_bucket, y = total.sulfur.dioxide , fill = quality_bucket),  data = wineRed) + 
        geom_boxplot() + scale_fill_brewer(type = 'seq', palette = 1)
       
#         stat_summary(fun.y=mean, geom="point", shape=5, size=3) 

pwS2 <- ggplot(aes(x = quality_bucket, y = free.sulfur.dioxide, fill = quality_bucket), data = wineRed) + 
        geom_boxplot() + scale_fill_brewer(type = 'seq', palette = 1)

sulfur <- wineRed$free.sulfur.dioxide + wineRed$total.sulfur.dioxide

pwS <- ggplot(aes(x = quality_bucket, y = sulfur, fill = quality_bucket), data = wineRed) + 
        geom_boxplot() + scale_fill_brewer(type = 'seq', palette = 1)

grid.arrange(pwS1, pwS2, pwS, ncol= 1)
```

Medium quality has more total sulfur dioxide and low quality has less sulfur.
I am not seing any correlation between the quality and the total sulfur.

Quality Vs Residual SUgar - Observed outliers in the midium and High quality
wine.

```{r echo=FALSE, Bivariate_Plots7}
ggplot(aes( x = quality_bucket , y = residual.sugar, fill = quality_bucket), data = wineRed) + 
        geom_boxplot() + scale_fill_brewer(type = 'seq', palette = 1) + 
        stat_summary(fun.y=mean, geom="point", shape=5, size=3)
```

# Bivariate Analysis

#### 1. Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

Looking at the ggcorr and ggpairs matrix, I observed some interesting 
relationships between the following variables:

We can see strong coorelation betwwen the following variable in the dataset
fixed acidity Vs density (0.7)
fixed acidity  Vs citric acid (0.7)
fixed acidity Vs pH (-0.7)
Alcohol Vs density (-0.5)
 
#### 2. Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
The density is strongly correlated with two other features: residual sugar 
(positively), and alcohol (negatively). It makes sense, taking into account the
fermentation process of wine, in which sugar is consumed to generate alcohol.

#### 3. What was the strongest relationship you found?
Percentage of Alcohol variable has the strongest relationship with quality. 
High quality wine has high alcohol % compare to medium and low. Increasing
percentage of Alcohol, the quality of the wine is high.

# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

ggplot(aes(x= residual.sugar , y = alcohol), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)
        

ggplot(aes(x= alcohol, y = density), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)


fa1 <- ggplot(aes(x= fixed.acidity , y = pH), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)
fa1

fa2 <- ggplot(aes(x= fixed.acidity , y = citric.acid), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)
fa2

fa3 <- ggplot(aes(x= fixed.acidity , y = density), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE)
fa3

```


1. Quality score is moving upward with increase of % of alcohol and residual
sugar. But one of the quality score-6 is varying from others. Which is moving
downward with increasing value of alcohol % and residual sugar.

2. Quality score moving downword with the increase of alcohol and decresing
of density.

3. Quality score is moving downward with pH and fixed acidity.

4. Quality score is moving upward with Citric acid and fixed acidity.

5. Quality score is moving upward with density and fixed acidity.


```{r echo=FALSE, Multivariate_Plots1}

wineRed$Quality <- as.numeric(wineRed$quality)

m1 <- lm(I(log(Quality)) ~ I(density^(1/3)), data = wineRed)
         
m2 <- update(m1, ~ . + alcohol)
m3 <- update(m2, ~ . + volatile.acidity)
m4 <- update(m3, ~ . + fixed.acidity)
m5 <- update(m4, ~ . + total.sulfur.dioxide)
m6 <- update(m5, ~ . + residual.sugar)
m7 <- update(m6, ~ . + citric.acid)

summary(m7)

```

# Multivariate Analysis

#### 1. Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?
I analyzed the relationship between quality and other feature variables in the
dataset. The alcohol,density and residual sugar had strong relationship with
each other and increasing the quality on the wine. I am seeing quality score
has a linear relationship with alcohol, volatile.acidity, fixed.acidity,
residual.sugar and citric.acid.

There are number of outliers for medium quality scores 5 & 6, also seeing small
number of ouliers for high quality score 7 & 8. I am seeing that the Quality 
increases when the % of alcohol increases. But, I am not seeing significant 
correlation from the linear model. I am seeing significant level of (p-value)
Pr = 0.908 for density and Pr = 0.999 for residual.sugar. These variables were
amongst the most important predictors in the linear model built.

#### 2. Were there any interesting or surprising interactions between features?
Yes, Quality is increases when the % of alcohol increases. But, I am not seeing
significant correlation from the linear model. 
95 percent confidence interval: 0.4373540  - 0.5132081

#### 3. OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.\

I created a linear model for predicting quality of wine. 
Adjusted R-squared:  0.2882, which is low. R-squard: 1 is strong in prediction.
It indicates that a linear model is not the best model for this dataset. 
The folowing Variables residual sugar, alcohol, citric acid, volatile acidity 
and density are influencing the prediction.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
wineRed$quality <- factor(wineRed$quality, ordered = T)


wineRed$quality_bucket <- ifelse(wineRed$quality <= 3,
                                 'Low Quality',
                                 ifelse(wineRed$quality <= 6,
                                        'Medium Quality',
                                        'High Quality'))
wineRed$quality_bucket <- ordered(wineRed$quality_bucket,
                     levels = c('Low Quality', 'Medium Quality', 'High Quality'))

ggplot(aes(x = quality_bucket), data = wineRed) + geom_bar(aes(fill = quality)) + scale_fill_brewer(type='seq') +
        xlab('Wine Quality') +
        ylab('Wine Count') +
        ggtitle('Quality Of Red Wine')

```

### Description One
Above ggplot tell us the industry producing Low, Medium and High Quality of 
Red wines. Also we can see the demand for the quality of the wine.
Medium wine are in more demand than High quality and Low quality red wine.  

### Plot Two
```{r echo=FALSE, Plot_Two}

pwaC <- ggplot(data = wineRed, aes(as.factor(quality), citric.acid, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("Citric Acid - g / dm^3")  +
        ggtitle("Quality Vs Citric.acid Vs") +
        scale_fill_brewer(type = 'seq', palette = 1) 
pwaC
pwaV <- ggplot(data = wineRed, aes(as.factor(quality), volatile.acidity, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("Volatile Acidity - g / dm^3)") + 
        ggtitle("Quality Vs Volatile.acidity") +
        scale_fill_brewer(type = 'seq', palette = 1)
pwaV
pwaF <- ggplot(data = wineRed, aes(as.factor(quality), fixed.acidity, fill = quality_bucket)) +
        geom_boxplot() +
        xlab("Quality") +
        ylab("Fixed Acidity - g / dm^3") + 
        ggtitle("Quality Vs Fixed.acidity") +
        scale_fill_brewer(type = 'seq', palette = 1)
pwaF
#grid.arrange( pwaC, pwaF, pwaV , ncol =1)

```

### Description Two
Analyzing the correlation of each acidity with quality. Red wine Quality is 
increasing with citric acid and fixed acidity but decreasing with volatile 
acidity. The fixed.acidity and citric.acid have highly correlated with quality
and positive impact at the same time volatile.acidity has negative impact on 
quality.The more acidity is better the quality of the red wine.

### Plot Three
```{r echo=FALSE, Plot_Three}

ggplot(aes(x= residual.sugar , y = alcohol), data = wineRed) +
        geom_point(aes(color = quality)) + scale_color_brewer(type = 'div',guide=guide_legend(reverse=TRUE)) +
        geom_smooth(aes(color = quality), method = "lm",level = 0.99, se=TRUE) +
        xlab('Residual Sugar (g / dm^3)') +
        ylab('Alcohol (% by volume)') +
        ggtitle('Quality of The Red Wine by Alcohol and Residual Sugar')

```

### Description Three
Looking at the plot, We can notice that the High Quality of the wine has more 
residual sugar and more alcohol and the trend is linearly upward. Low quality 
wine has less residualsugar and % of alcohol is also less and the quality trend
is linearly upward. Medium quality wine has an interesting behaviour, It has 
more residual sugar and the trend is lenear. But I am seeing 2 different 
linearlity. Scored 5 one is positive or in upward direction with alcohol 
and residual sugar, but the score 6 one is in negative or in downward direction.

# Reflection
This explores the univariate, bivariate, & multivariate relationships between
variables. This data set contains 1,599 red wines with 11 variables on the 
chemical properties of the wine.

Residual Sugar - This is the amount of sugar left in solution after fermentation
has finished. Residual sugar and density have a positive strong correlation.
R-squard: Pr values 0.99 and 0.91 accordingly. In wine tasting, the term
"acidity" refers to the fresh, tart and sour attributes of the wine which are
evaluated in relation to how well the acidity balances out the sweetness and
bitter components of the wine. I identified Residual sugar, Alcohol, Acidity
and Density are strongly correlated togheter influencing the quality of the
wine. Alcohol content appeared to be the number one factor for determining a
high quality wine. Citric acid and Sulphates had to be in specific amounts 
in order for alcohol to influence the taste or quality of the wine.

I observed, Wine with high percent of alcohol content and total acidity 
tends to be rated as high quality wine. Also wine with low % of alcohol with 
more total acidity tends to be rated as low quality wine. Based on the result,
we can see that the acidity in wine and percent of alcohol content are two 
important components in the quality and taste of Red wine.

Red wines have deep colors, full bodied, stronger, concentrated flavors and
smooth mouthfeel tend to stand out from the assortment more than wines with
more subtle characteristics. The process of evaluating wines is very subjective,
and experts can be biased by their histories and preferences. It is too complex
to make the relation between quality and the other variables using the linear 
model. Therefore in furture, I think, there are better models or methods 
(Decision tree learning methods) can be use. We can use machine learning to 
clasify the quality of wine.

References:

https://classroom.udacity.com/nanodegrees/nd002/parts/0021345407

https://www.statmethods.net/

https://briatte.github.io/ggcorr/#controlling-the-coefficient-labels

https://en.wikipedia.org/wiki/Acids_in_wine
